---
title: "Milestone Report 1"
author: "Sara Regina Ferreira de Faria"
date: "22/10/2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Download and Load Data

```{r, eval=FALSE}
download.file("https://d396qusza40orc.cloudfront.net/dsscapstone/dataset/Coursera-SwiftKey.zip", "data.zip")

con <- file("final/en_US/en_US.twitter.txt", "r") 
twitter <- readLines(con) 
close(con)

con <- file("final/en_US/en_US.blogs.txt", "r") 
blogs <- readLines(con) 
close(con)

con <- file("final/en_US/en_US.news.txt", "r") 
news <- readLines(con) 
close(con)
```

## Summary about the data set

explain the major features of the data. 
basic summaries of the three files
Word counts, line counts and basic data tables

## Findings on the data set

basic plots, such as histograms to illustrate features of the data?

## Plans for prediction algorithm and Shiny App

plans for creating the prediction algorithm and Shiny app 
understandable to a non-data scientist manager.
