---
title: "Task4"
author: "Sara Regina Ferreira de Faria"
date: "27/09/2018"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Build Model using Markov Chains

"The Markov Property states that the probability of future states depends only on the present state, not on the sequence of events that preceded it" https://sookocheff.com/post/nlp/ngram-modeling-with-markov-chains/

http://rstudio-pubs-static.s3.amazonaws.com/145695_54511af736d945a0a09101536f34aeb6.html#/

http://www.cs.cornell.edu/courses/cs4740/2014sp/lectures/smoothing+backoff.pdf


https://www.datacamp.com/community/tutorials/markov-chain-analysis-r
https://dataconomy.com/2018/03/an-introduction-to-markov-chains-using-r/

http://rpubs.com/Lalithah/milestonereport
https://nohahady.github.io/the-report/the_report.html
http://rpubs.com/khadar/456438

```{r}
library(diagram)
library(markovchain)

DriverZone <- c("North", "South", "West")
ZoneTransition <- matrix(c(0.3,0.3,0.4,0.4,0.4,0.2,0.5,0.3,0.2), nrow=3, byrow=T, dimname = list(DriverZone, DriverZone))

McZone <- new("markovchain", states = DriverZone, byrow = T, transitionMatrix = ZoneTransition, name = "Driver Movement")

plotmat(ZoneTransition, pos=c(1,2), lwd=1)

sequence <- c("a", "b", "a", "a", "a", "a", "b", "a", "b", "a", 
              "b", "a", "a", "b", "b", "b", "a")
mcFit <- markovchainFit(data=sequence)

```

## How does the model perform for different choices of the parameters and size of the model?



## How much does the model slow down for the performance you gain?



## Does perplexity correlate with the other measures of accuracy?



## Can you reduce the size of the model (number of parameters) without reducing performance?

